SOMETHING ABOUT THE DISTRIBUTED AVERAGING BASED APPROXIMATION IN SENSOR NETWORKS

### 2022-10-18 paper.tex
version for Toon,Randy

\section[]{Conclusions}
\label{sec:conclusions}
In this contribution, we propose an extension to a distributed adaptive BSI algorithm applied in sensor networks.
Based on distributed averaging, only using the information provided by neighboring nodes in the sensor network, we compute estimates of norm values of channel estimates in order to enforce a norm constraint.
By balancing the averaging with introducing new data into the recursion, we allow the algorithm to follow an adaptive updating scheme.
The mixing factor, which balances new data with recursion data, is set adaptively dependent on instantaneous channel estimate norms.
These introductions reduce inter-node transmissions for each time frame while still delivering steady-state estimation performance close to the optimal case where network-wide information is available at all nodes.
The reduction that can be achieved goes as far as only needing a single iteration and, therefore, one additional inter-neighborhood information exchange per time frame.
We show this in simulations with a white Gaussian input signal and random impulse responses drawn from the normal distribution.
\begin{todo}
    Could use the little space that's left for an illustration in the beginning or something. Or add a comparison of numbers put into \autoref{tab:transcost:table} for different setups varying \(M,N_i,K\).
\end{todo}

>>>>

\section[]{Conclusions}
\label{sec:conclusions}
In this contribution, we propose an extension to a distributed adaptive BSI algorithm applied in sensor networks.
Based on distributed averaging, only using the information provided by neighboring nodes in the sensor network, we compute estimates of norm values of channel estimates in order to enforce a norm constraint.
By balancing the averaging with introducing new data into the recursion, we allow the algorithm to follow an adaptive updating scheme.
The mixing factor, which balances new data with recursion data, is set adaptively dependent on instantaneous channel estimate norms.
These introductions reduce inter-node transmissions for each time frame while still delivering steady-state estimation performance close to the optimal case where network-wide information is available at all nodes.
The reduction that can be achieved goes as far as only needing a single iteration and, therefore, one additional inter-neighborhood information exchange per time frame.
We show this in simulations with a white Gaussian input signal and random impulse responses drawn from the normal distribution.
\begin{todo}
    \begin{itemize}
        \item Could use the little space that's left for an illustration in the beginning or something.
        \item Or add a comparison of numbers put into \autoref{tab:transcost:table} for different setups varying \(M,N_i,K\).
        \item Can increase \(L\) for simulations, not sure if necessary to show what the extension does.
    \end{itemize}
\end{todo}
